---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# getMFdata

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/morner75/getMFdata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/morner75/getMFdata/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`getMFdata` is an R package for retrieving macro-financial data from Korean public institutions and international organizations through their official APIs.

| Source | Organization | Auth |
|--------|-------------|------|
| **ECOS** | Bank of Korea (한국은행) | API key required |
| **FISIS** | Financial Supervisory Service (금융감독원) | API key required |
| **IMF** | International Monetary Fund | Public |
| **OECD** | Organisation for Economic Co-operation and Development | Public |
| **BIS** | Bank for International Settlements | Public |

Originally developed for stress-testing workflows at the Financial Supervisory Service, the package aims to provide a consistent interface across heterogeneous data sources.

## Installation

```r
# install.packages("devtools")
devtools::install_github("morner75/getMFdata")
```

## API Keys

ECOS and FISIS require API keys. Store them in your `.Renviron` file so they are available across sessions:

```r
# Open .Renviron for editing
usethis::edit_r_environ()
```

Add the following lines and restart R:

```
ECOS_key=your_ecos_key_here
FISIS_key=your_fisis_key_here
```

- **ECOS key**: register at <https://ecos.bok.or.kr/api/>
- **FISIS key**: register at <https://fisis.fss.or.kr/openapi/>

---

## ECOS — Bank of Korea

```{r ecos-setup, message=FALSE}
library(getMFdata)
library(dplyr)

ECOS_key <- Sys.getenv("ECOS_key")
```

### Search for statistics codes

`ecosSearch()` searches across ~52,000 item entries (Korean and English names) bundled with the package — no API call needed.

```{r ecos-search}
# Find codes related to GDP
ecosSearch("GDP") |> select(STAT_CODE, STAT_NAME, ITEM_CODE, ITEM_NAME, CYCLE) |> head(5)
```

```{r ecos-search-kr}
# Korean keyword search
ecosSearch("소비자물가") |> select(STAT_CODE, STAT_NAME, ITEM_CODE, ITEM_NAME, CYCLE) |> head(5)
```

### Browse available statistics tables

```{r ecos-list, eval=FALSE}
# Returns all ~600 statistics tables
getEcosList(ECOS_key)
```

### Inspect item codes for a table

```{r ecos-code}
# Item structure for table 722Y001 (BOK base rate and lending/deposit rates)
getEcosCode(ECOS_key, "722Y001") |> select(ITEM_CODE, ITEM_NAME, CYCLE, START_TIME, END_TIME)
```

### Retrieve data

`getEcosData()` returns a two-column tibble of `TIME` and `DATA_VALUE`.

```{r ecos-data}
# BOK base rate, monthly, 2020–2024
getEcosData(ECOS_key, "722Y001", "M", "202001", "202412", "0101000", "", "")
```

### Format date parameters with `EcosTerm()`

`EcosTerm()` converts R date objects to the period strings ECOS expects.

```{r ecos-term}
EcosTerm(Sys.Date(), "A")   # annual:    e.g. "2026"
EcosTerm(Sys.Date(), "Q")   # quarterly: e.g. "2026Q1"
EcosTerm(Sys.Date(), "M")   # monthly:   e.g. "202603"
EcosTerm(Sys.Date(), "D")   # daily:     e.g. "20260322"
```

---

## FISIS — Financial Supervisory Service

FISIS provides balance sheet and income statement data for Korean financial institutions.

```{r fisis, eval=FALSE}
FISIS_key <- Sys.getenv("FISIS_key")

# List financial institutions
getFsisInfos(FISIS_key, "companySearch")

# List available statistics
getFsisInfos(FISIS_key, "statisticsListSearch", item_code = "A")

# Retrieve bank balance sheet data (annual, 2015–2023)
getFsisData(FISIS_key,
            finance_cd  = "0010001",  # all banks
            list_no     = "SA053",    # balance sheet
            account_cd  = "B",
            term        = "Y",
            start_month = "201501",
            end_month   = "202312")
```

---

## IMF — International Monetary Fund

`getImfData()` queries the IMF IFS SDMX-JSON API. `processImfData()` converts the raw response to a tidy data frame.

```{r imf, eval=FALSE}
# CPI inflation (annual) for Korea and the US, 2010–2023
imf_raw <- getImfData(
  indicator_code = "PCPI_PC_CP_A_PT",
  countries      = c("KR", "US"),
  start_date     = "2010-01-01",
  end_date       = "2023-01-01",
  frequency      = "A"
)

processImfData(imf_raw)
#> # A tibble: 28 × 3
#>   country time  value
#>   <chr>   <chr> <chr>
#> 1 KR      2010  2.94 ...
```

---

## OECD

`getOecdDB()` fetches data from any OECD SDMX-JSON endpoint and returns raw `structure` and `dataSets` list components.

```{r oecd, eval=FALSE}
# Korean real GDP, quarterly seasonally adjusted
url <- paste0(
  "https://stats.oecd.org/SDMX-JSON/data/",
  "QNA/KOR.B1_GE.LNBQRSA.Q/all?startTime=2000-Q1"
)
result <- getOecdDB(url)

# Dimension labels
result$structure$dimensions$observation
# Observations
result$dataSets[[1]]$observations |> head()
```

---

## BIS — Bank for International Settlements

`getBisDB()` scrapes the BIS full data sets page and returns a tibble of dataset names and download URLs. `getBisData()` downloads and reads a ZIP file into R.

```{r bis-db}
# List available BIS datasets
db <- getBisDB()
db
```

```{r bis-data, eval=FALSE}
# Download consumer prices dataset
cpi_raw <- db |>
  filter(name == "Consumer prices") |>
  pull(url) |>
  getBisData(quiet = TRUE)

# Filter: annual, all countries, CPI index (771)
cpi_raw |>
  filter(stringr::str_detect(Series, "^A.+771$")) |>
  select(REF_AREA, `Reference area`, matches("^20[0-9]{2}$")) |>
  head()
```

---

## Bundled dataset

`usdkrw` — monthly average USD/KRW exchange rate from January 1990 to the present, loaded lazily.

```{r usdkrw}
head(usdkrw)
tail(usdkrw)
```
