---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# getMFdata

<!-- badges: start -->
<!-- badges: end -->

The goal of `getMFdata` package is to provide a tool of facilitating **retrieving Macro-Finance data from official APIs** in Korea's public institutions and international orgainisations.  Currently, the package consist of main wrapper functions for connecting **ECOS** (Bank of Korea), **FISIS** (Financial Supervisory Service), **KOSIS** (Statistics Korea), **FRED** (Federal Reserve Bank of St. Louis), **IMF** (International Monetary Fund), **OECD** (Organisation for Economic Co-operations and Development), **BIS** (Bank of International Settlement). 

The `getMFdata` was initially developed for internal use in Financial Supervisory Service to fetch macroeconomic data for stress-testing.
This package is still under development and aims to take a balance between ease to use and flexibility  to accommodate varioous data structures.  

## Installation

You can install the development version of getMFdata like so:

``` r
library(devtools)
install_github("morner75/getMFdata")
```

## Example

The following are basic examples which show you how to retrieve data from BOK and BIS sources. 
Some sources requires your API authentication before you can get access to data.

```{r example}
library(getMFdata)
library(stringr)
suppressMessages(library(dplyr))

## 1. BOK ECOS data

# ECOS API key
ECOS_key <- Sys.getenv(x="ECOS_key")

# Retrieve data 
# data : 200Y001 국민소득통계 연간지표 실질경제성장율
ecos_df <- getEcosData(ECOS_key,"200Y001","A", "1980","2022", "20101","?","?")
head(ecos_df)


## 2. BIS data

# get BIS database
bisDB <- getBisDB()  

# Retrieve data : consumer price
bisData <-        
  bisDB %>% 
  filter(name=="Consumer prices") %>% 
  pull() %>% 
  getBisData()

# Data processing 
CPI <- bisData %>% 
  filter(str_detect(Series,"^A.+771$")) %>% 
  select(REF_AREA, `Reference area`, matches("^20[0-9]{2}$"))

head(CPI)



```




