---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# getMFdata

<!-- badges: start -->
<!-- badges: end -->


### Retrieving macro-financial data from offical APIs


The goal of the `getMFdata` package is to facilitate the retrieval of Macro-Finance data from official APIs in Korea's public institutions and international organizations. The package currently consists of main wrapper functions that enable connection to **ECOS** (Bank of Korea), **FISIS** (Financial Supervisory Service), **KOSIS** (Statistics Korea), **FRED** (Federal Reserve Bank of St. Louis), **IMF** (International Monetary Fund), **OECD** (Organization for Economic Co-operation and Development), and **BIS** (Bank of International Settlement). 

Initially developed for internal use in the Financial Supervisory Service to fetch macroeconomic data for stress-testing, the `getMFdata` package is still under development and aims to balance ease of use with flexibility to accommodate various data structures. 


### Installation

To install the package, please follow standard R package installation procedures.

``` r
library(devtools)
install_github("morner75/getMFdata")
```

### Example

The following are basic examples which show you how to retrieve data from BOK and BIS sources. 
Some sources requires your API authentication before you can get access to data.

```{r example}
library(getMFdata)
library(stringr)
suppressMessages(library(dplyr))

## 1. BOK ECOS data

# ECOS API key
ECOS_key <- Sys.getenv(x="ECOS_key")

# Retrieve data 
# data : 200Y001 국민소득통계 연간지표 실질경제성장율
ecos_df <- getEcosData(ECOS_key,"200Y001","A", "1980","2022", "20101","?","?")
head(ecos_df)


## 2. BIS data

# get BIS database
bisDB <- getBisDB()  

# Retrieve data : consumer price
bisData <-        
  bisDB %>% 
  filter(name=="Consumer prices") %>% 
  pull() %>% 
  getBisData()

# Data processing 
CPI <- bisData %>% 
  filter(str_detect(Series,"^A.+771$")) %>% 
  select(REF_AREA, `Reference area`, matches("^20[0-9]{2}$"))

head(CPI)



```




