---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# getMFdata

<!-- badges: start -->
<!-- badges: end -->

The goal of `getMFdata` package is to provide a tool of facilitating **retrieving Macro-Finance data from official APIs** in Korea's public institutions and international orgainisations. This package was initially developed for internal use in Financial Supervisory Service to fetch macroeconomic data for stress-testing. Currently, `getMFdata` consist of main wrapper functions for connecting **ECOS** (Bank of Korea), **FISIS** (Financial Supervisory Service), **KOSIS** (Statistics Korea), **FRED** (Federal Reserve Bank of St. Louis), **IMF** (International Monetary Fund), **OECD** (Organisation for Economic Co-operations and Development), **BIS** (Bank of International Settlement). This package is still under development for balancing simplicity and flexibility.  

## Installation

You can install the development version of getMFdata like so:

``` r
library(devtools)
install_github("morner75/getMFdata")
```

## Example

This is a basic example which shows you how to retrieve data from various source. 
Some sources requires your API authentication before you can get access to data.

```{r example}
library(getMFdata)
library(stringr)
suppressMessages(library(dplyr))

## 1. BOK ECOS data

# ECOS API key
ECOS_key <- Sys.getenv(x="ECOS_key")

# Retrieve data 
# data : 200Y001 국민소득통계 연간지표 실질경제성장율
ecos_df <- getEcosData(ECOS_key,"200Y001","A", "1980","2022", "20101","?","?")
head(ecos_df)


## 2. BIS data

# get BIS database
bisDB <- getBisDB()  

# Retrieve data : consumer price
bisData <-        
  bisDB %>% 
  filter(name=="Consumer prices") %>% 
  pull() %>% 
  getBisData()

# Data processing 
CPI <- bisData %>% 
  filter(str_detect(Series,"^A.+771$")) %>% 
  select(REF_AREA, `Reference area`, matches("^20[0-9]{2}$"))

head(CPI)



```




